Comparison with Christensen paper

### 2018-12-17 paper-comparison/compare-christensen.Rmd
Paper cpt favors 5 cpts

@@

>>>>

```{r save LDAs}
save(ldamodel, file = 'paper_lda.Rds')
save(ldats_lda_selected, file = 'ldats_lda.Rds')
```

@@

<!-- skip for now due to error -->
<!-- ```{r LDATS changepoint} -->

<!-- ldats_cpt_paper_lda <- LDATS::TS_on_LDA(LDA_models = ldamodel, rodents[[2]], -->
<!--                                         formulas =c( '~ sin_year + cos_year'), nchangepoints = c(2, 3, 4, 5, 6)) -->

<!-- ``` -->

```{r paper changepoint on LDATS lda}
source('christensen-ecology-files/changepointmodel.r')
# set up parameters for model
year_continuous = 1970 + as.integer(julian(ch_dates)) / 365.25
x = data.frame(
  year_continuous = year_continuous,
  sin_year = sin(year_continuous * 2 * pi),
  cos_year = cos(year_continuous * 2 * pi)
)

# run models with 1, 2, 3, 4, 5 changepoints
cp_results_rodent = changepoint_model(ldats_lda_selected[[1]], x, 1, weights = rep(1,length(year_continuous)))
cp_results_rodent2 = changepoint_model(ldats_lda_selected[[1]], x, 2, weights = rep(1,length(year_continuous)))
cp_results_rodent3 = changepoint_model(ldats_lda_selected[[1]], x, 3, weights = rep(1,length(year_continuous)))
cp_results_rodent4 = changepoint_model(ldats_lda_selected[[1]], x, 4, weights = rep(1,length(year_continuous)))
cp_results_rodent5 = changepoint_model(ldats_lda_selected[[1]], x, 5, weights = rep(1,length(year_continuous)))
cp_results_rodent6 = changepoint_model(ldats_lda_selected[[1]], x, 6, weights = rep(1,length(year_continuous)))

save.image(file = '/Users/renatadiaz/Desktop/paper_cpt_ldats_lda.Rdata')

# change point model selection
# mean deviance ( -2 * log likelihood) + 2*(#parameters)
mean(cp_results_rodent$saved_lls * -2) + 2*(3*(ntopics-1)*(1+1)+(1))
mean(cp_results_rodent2$saved_lls * -2)+ 2*(3*(ntopics-1)*(2+1)+(2))
mean(cp_results_rodent3$saved_lls * -2)+ 2*(3*(ntopics-1)*(3+1)+(3))
mean(cp_results_rodent4$saved_lls * -2)+ 2*(3*(ntopics-1)*(4+1)+(4))
mean(cp_results_rodent5$saved_lls * -2)+ 2*(3*(ntopics-1)*(5+1)+(5))

The lowest deviance (1215.971) is for 5 changepoints!

Running one with 6.
